From OpenACC to OpenMP 4: \\ Toward Automatic Translation

### 2016-06-09 paper.tex
Added ACM copyright text
Fixed spelling errors

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{}

% ISBN
\isbn{}

%Conference
\conferenceinfo{XSEDE '16}{July 17--21, 2016, Miami, FL, USA}

\acmPrice{\$15.00}

@@

%Several directive-based GPU programming models have been proposed over the year to characterize parallel program. 
Lee and Vetter~\cite{lee2012early} evaluate existing directive-based models and
show that directive-based models can achieve reasonable performance compared to
hand-written GPU codes. For accelarator programming, the two most promising
options are OpenACC and OpenMP.  Wienke et al.~\cite{wienke2014pattern} compare
both models with respect to their programmability to assist developers in
deciding which approach to take.  Xu and colleagues~\cite{xu2013exploring}
demonstrate the effectiveness of a hybrid model combined with OpenACC and
OpenMP as a plausible solution to port scientific applications in heterogeneous
architectures.

@@

We have described an algorithm (\S\ref{sec:algorithm}) and a prototype tool
that converts a subset of OpenACC (Figure~\ref{fig:grammar}) to OpenMP~4.  The
translation algorithm was designed to be simple and predicatble, since it will
necessarily be used in conjunction with manual restructuring and performance
tuning.  We evaluated our tool by converting the EPCC Level~1 OpenACC
benchmarks from OpenACC compiled by PGI C/C++ to OpenMP~4 compiled by Clang.
Both targeted an NVIDIA GPU (Tesla~K40).  To keep the translation process
transparent, the programmer was required to manually convert OpenACC
\emph{kernels} loops, although the tool was able to automatically translate the
remaining 67 of 70 directives.

>>>>

% Copyright
\CopyrightYear{2016}
\setcopyright{acmlicensed}
\conferenceinfo{XSEDE16,}{July 17 - 21, 2016, , }
\isbn{978-1-4503-4755-6/16/07}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2949550.2949654}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{}

% ISBN
%\isbn{}

%Conference
%\conferenceinfo{XSEDE '16}{July 17--21, 2016, Miami, FL, USA}

%\acmPrice{\$15.00}

@@

%Several directive-based GPU programming models have been proposed over the year to characterize parallel program. 
Lee and Vetter~\cite{lee2012early} evaluate existing directive-based models and
show that directive-based models can achieve reasonable performance compared to
hand-written GPU codes. For accelerator programming, the two most promising
options are OpenACC and OpenMP.  Wienke et al.~\cite{wienke2014pattern} compare
both models with respect to their programmability to assist developers in
deciding which approach to take.  Xu and colleagues~\cite{xu2013exploring}
demonstrate the effectiveness of a hybrid model combined with OpenACC and
OpenMP as a plausible solution to port scientific applications in heterogeneous
architectures.

@@

We have described an algorithm (\S\ref{sec:algorithm}) and a prototype tool
that converts a subset of OpenACC (Figure~\ref{fig:grammar}) to OpenMP~4.  The
translation algorithm was designed to be simple and predictable, since it will
necessarily be used in conjunction with manual restructuring and performance
tuning.  We evaluated our tool by converting the EPCC Level~1 OpenACC
benchmarks from OpenACC compiled by PGI C/C++ to OpenMP~4 compiled by Clang.
Both targeted an NVIDIA GPU (Tesla~K40).  To keep the translation process
transparent, the programmer was required to manually convert OpenACC
\emph{kernels} loops, although the tool was able to automatically translate the
remaining 67 of 70 directives.
